SPARQL on the Open, Decentralised Web

### 2016-07-22 dissertation/motivation.tex
more Helens corrections

While a failure to be developer friendly may be one reason why the
Semantic Web has not succeeded at a grand scale, my training in
natural science lead me to ask if there may be other reasons that we
do not see the remarkable rate of progress of the natural sciences in
this field. These questions are as hard to ask and to live with as to
answer.

I became early quite confident that the practice of benchmarking was
an easy target, with its lack of summary statistics and inability to
support proper hypothesis testing, standardising to deal with
complexity rather than methodological advances, and lack of ability to
formulate the experiment as severe enough.

@@

Clearly, the above motivation points out federated SPARQL as a key
solution to the problem of query answering over decentralised sources,
and that was originally where I intended my main contributions. During
the work, it became clear that the stability of individual endpoints
would need to addressed first. In the detailed problem descriptions,
this will be further discussed as the choice of caching as a point of
focus is somewhat arbitrary.

An important motivation was not problems, however, but opportunity:
The proliferation of Content Delivery Networks is an opportunity for
improvement, the emergence of Triple Pattern Fragments, and traits
based planning in Section~\ref{sec:conpush} all represent important
opportunities to seize.

>>>>

While a failure to be developer friendly may be one reason why the
Semantic Web has not succeeded on a grand scale, my training in
natural science lead me to ask if there may be other reasons that we
do not see the remarkable rate of progress of the natural sciences in
this field. These questions are as hard to ask and to live with as to
answer.

I became early quite confident that the practice of benchmarking was
an easy target, with its lack of summary statistics and inability to
support proper hypothesis testing, standardising to deal with
complexity rather than methodological advances, and lacking in ability to
formulate the experiment as severe enough.

@@

Clearly, the above motivation points out federated SPARQL as a key
solution to the problem of query answering over decentralised sources,
and that was originally where I intended my main contributions. During
the work, it became clear that the stability of individual endpoints
would need to addressed first. This will be further discussed in the
detailed problem descriptions, as the choice of caching as a point of
focus is somewhat arbitrary.

An important motivation was not problems, however, but opportunity:
The proliferation of Content Delivery Networks was an opportunity for
improvement, the emergence of Triple Pattern Fragments, and traits
based planning in Section~\ref{sec:conpush} all represented important
opportunities to seize.
